### 2016-11-25 local-capability-machine.tex
Added comment in scall
Changed scall

@@

  \item Return address: Clear the stack segment we gave control over

@@

@@

    \item [Clear the stack segment we gave control over] Store 0 to all the cells the stack capability passed to the callee governed.

@@

\begin{figure}
  \label{fig:stack-after-restrict-and-zero}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Stack} \\
\cline{2-2}
   & \\
   & $\vdots$\\
\cline{2-2}
$c_{\var{stk}}'' \rightarrow$  & $c_{\var{stk}}'$ \\
\cline{2-2}
   & $c_\pc'$ \\
\cline{2-2}
   & $c_0$ \\
\cline{2-2}
   & $w_{p,1}$ \\
\cline{2-2}
   & $\vdots$ \\
\cline{2-2}
   & $w_{p,m}$ \\
\cline{2-2}
$c_0' \rightarrow$   & Restore code \\
   & $\vdots$\\
\cline{2-2}
   & local stack\\
   & $\vdots$\\
\cline{2-2}
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_{\pc}^{(3)}$\\
\cline{2-2}
$r_0$  & $c_0'$ \\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}''$ \\
\cline{2-2}
$r_{\var{args},1}$ & $w_{a,1}$ \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{args},n}$ & $w_{a,n}$\\
\cline{2-2}
$r_{\var{priv},1}$ & 0\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & 0 \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{ Stack and register-file after the $c_{\var{stk}}'$ has been limited to only give authority over the empty part of the stack (the new capability is $c_{\var{stk}}''$). $c_0'$ is made from $c_{\var{stk}}'$ by setting it to point to the restore code and restricting it to a local enter-capability. The ``private'' registers have been cleared.}
\end{figure}

@@

\begin{figure}
  \label{fig:stack-after-restore-code}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Stack} \\
\cline{2-2}
   & \\
   & $\vdots$\\
\cline{2-2}
   & 0 \\
\cline{2-2}
$c_{\var{stk}} \rightarrow$   & local stack\\
   & $\vdots$\\
\cline{2-2}
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_\pc^{(3)}$\\
\cline{2-2}
$r_0$  &  $c_0$ \\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}$ \\
\cline{2-2}
$r_1$ & $w_1$ \\
\cline{2-2}
$r_{\var{priv},1}$ & $w_{p,1}$\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & $w_{p,m}$ \\
\cline{2-2}
& $?$ \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{ Stack and register-register file after the clean up code has been run. The untrusted part of the stack has been cleared. The ``private'' words have been poped to their respective registers. The restore code has been poped of the stack. The stack is now in the same state as it was before the call. }
\end{figure}

>>>>

  \item Clear the stack we release control over

@@

  \item Return address: 

@@

  \item [Clear the stack we release control over]
    Store 0 to all the memory cells the restricted stack pointer has authority over.

@@

@@

\begin{figure}
  \label{fig:stack-after-restrict-and-zero}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Stack} \\
\cline{2-2}
   & \\
   & $\vdots$\\
\cline{2-2}
   & $?$\\
\cline{2-2}
$c_{\var{stk}}'' \rightarrow$  & $c_{\var{stk}}'$ \\
\cline{2-2}
   & $c_\pc'$ \\
\cline{2-2}
   & $c_0$ \\
\cline{2-2}
   & $w_{p,1}$ \\
\cline{2-2}
   & $\vdots$ \\
\cline{2-2}
   & $w_{p,m}$ \\
\cline{2-2}
$c_0' \rightarrow$   & Restore code \\
   & $\vdots$\\
\cline{2-2}
   & local stack\\
   & $\vdots$\\
\cline{2-2}
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_{\pc}^{(3)}$\\
\cline{2-2}
$r_0$  & $c_0'$ \\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}''$ \\
\cline{2-2}
$r_{\var{args},1}$ & $w_{a,1}$ \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{args},n}$ & $w_{a,n}$\\
\cline{2-2}
$r_{\var{priv},1}$ & 0\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & 0 \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{ Stack and register-file after the $c_{\var{stk}}'$ has been limited to only give authority over the empty part of the stack (the new capability is $c_{\var{stk}}''$). The empty part of the stack has been cleared. $c_0'$ is made from $c_{\var{stk}}'$ by setting it to point to the restore code and restricting it to a local enter-capability. The ``private'' registers have been cleared.}
\end{figure}

@@

\begin{figure}
  \label{fig:stack-after-restore-code}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
\multicolumn{2}{l}{Stack} \\
\cline{2-2}
   &  \\
   & $\vdots$ \\
\cline{2-2}
   & ?\\
\cline{2-2}
   & 0 \\
\cline{2-2}
   & $\vdots$\\
\cline{2-2}
   & 0 \\
\cline{2-2}
$c_{\var{stk}} \rightarrow$   & local stack\\
   & $\vdots$\\
\cline{2-2}
\end{tabular}
\hspace{1cm}
\begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
\multicolumn{2}{r}{Register file} \\
\cline{2-2}
$\pcreg$ & $c_\pc^{(3)}$\\
\cline{2-2}
$r_0$  &  $c_0$ \\
\cline{2-2}
$r_{\var{stk}}$  & $c_{\var{stk}}$ \\
\cline{2-2}
$r_1$ & $w_1$ \\
\cline{2-2}
$r_{\var{priv},1}$ & $w_{p,1}$\\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
$r_{\var{priv},m}$ & $w_{p,m}$ \\
\cline{2-2}
& $?$ \\
\cline{2-2}
& $\vdots$ \\
\cline{2-2}
\end{tabular}
\caption{ Stack and register-register file after the clean up code has been run. The ``private'' words have been poped to their respective registers. The restore code has been poped of the stack. }
\end{figure}
